\documentclass[11pt,a4paper]{article}
\usepackage[left=2cm,right=2cm,top=1cm,bottom=1cm]{geometry}
\pagestyle{empty}

\usepackage{datetime}
%\usepackage[yyyymmdd,hhmmss]{datetime}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{enumitem}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage{xcolor}
\usepackage[colorlinks=true]{hyperref}

\newcommand{\TODO}[1]{\textcolor{red}{*** #1 ***}}

\begin{document}

\begin{center}
{\huge\textbf{Program of the GAP Days 2014, August 25-29}\\[2mm]}
Version from \today\ at \currenttime\\[2mm]
Talks are at \href{https://maps.google.com/maps?q=Pontdriesch+14,+Aachen,+Germany&hl=en&ll=50.778617,6.080579&spn=0.004993,0.008969&sll=37.0625,-95.677068&sspn=50.777825,73.476563&oq=pontdriesch+14+&hnear=Pontdriesch+14,+Mitte+52062+Aachen,+Germany&t=m&z=17}{Pontdriesch 14/16}
in room 008, coding sessions in rooms 003 and 103.
\end{center}

% \vortrag{TIME}{AUTHOR}{TITLE}
\newcommand{\vortrag}[3]{#1 & #2 \\ & \textit{#3} \\}
%\newcommand{\vortrag}[3]{#1 & #2: ``\textit{#3}'' \\}

\newcommand{\newday}[1]{\multicolumn{2}{c}{{\large\textbf{#1}}} \\[1em]}


\begin{tabular}{rp{14.5cm}}
%
\newday{Monday, August 25}
10:00 & Coding session and discussion \\
14:00 & Welcome session (room 008) \\
\vortrag{15:00}{Vinay Wagh}{\href{https://github.com/homalg-project/LessGenerators}{LessGenerators} -- finding small generating sets for modules (part of the homalg project)}
\vortrag{15:30}{Martin Bies}{String theory, sheaf cohomology and the homalg package}
\vortrag{16:00}{Johannes Hahn}{Coxeter groups and Kazhdan-Lusztig theory in GAP}
\vortrag{16:30}{Chris Jefferson}{Ferret -- a modern C++ rewrite of Partition Backtracking in GAP}
\vortrag{17:00}{Max Horn}{\href{http://gap-system.github.io/libsing/}{libsing} -- an interface between \href{http://www.singular.uni-kl.de/}{Singular} and GAP}
\vortrag{17:30}{Christof Söger}{\href{https://github.com/fingolfin/NormalizInterface}{NormalizInterface} -- an interface between \href{http://www.math.uos.de/normaliz}{normaliz} and GAP}
%
%
\\
%
%
\newday{Tuesday, August 26}
\vortrag{10:00}{Sebastian Gutsche \& Max Horn}{How to make a GAP package}
\vortrag{16:00}{Pedro A. García-Sánchez
}{Recent progress in the \href{http://www.gap-system.org/Packages/numericalsgps.html}{NumericalSgps} package}
\vortrag{16:30}{Manual Delgado}{\href{http://www.gap-system.org/Packages/intpic.html}{intpic} -- a package for drawing integers, by emphasizing some subsets.}
\vortrag{17:00}{Hebert Perez-Roses}{Graph construction via voltage assignment with GAP}
\vortrag{17:30}{Delaram Kahrobaei}{TBA}
%
%
\\
%
%
\newday{Wednesday, August 27}
\vortrag{10:00}{Reimer Behrends}{HPC-GAP: Design and Implementation of a Concurrency Model for GAP}
\vortrag{16:20}{Markus Pfeiffer}{Two (HPC)GAP infrastructure packages in the making: GAPData and Matrix}
\vortrag{16:50}{Sebastian Gutsche \& Sebastian Posur}{ToolsForHomalg - Tools for caching and propagation \& CategoriesForHomalg - A GAP-based meta language for category theory based computations}
\vortrag{17:30}{Thomas Breuer}{Recent progress concerning the GAP packages AtlasRep, CTblLib, CTBlocks, MFER}

19:00 & Dinner at the ``\href{http://www.labyrinthaachen.de/}{Labyrinth}'' \\
%
%
\\
%
%
\newday{Thursday, August 28}
\vortrag{10:00}{Alexander Konovalov}{Continuous integration, package update mechanism and release management in GAP}
%
%
\\
%
%
\newday{Friday, August 29}
10:00 & Open discussion: Your wishes for the future of GAP \\ 
13:30 & Open discussion: Results of the meeting, feedback \\

\end{tabular}

\vfill

\begin{center}
  \url{http://gapdays2014.coxeter.de/}
\end{center}


\pagebreak


% \Abstract{NAME}{AFFIL}{TITLE}
%\newenvironment{Abstract}[3]{\noindent\textbf{#1} (#2) \\ \noindent \textit{#3} \\ \noindent  \par{} \noindent}{\bigskip}
\newenvironment{Abstract}[3]{\begin{itemize}[itemsep=0mm,label={}]
  \item \textbf{#1} (#2)
  \item ``\textit{#3}''
  \item}{\end{itemize}\medskip}


%\begin{center}
{\noindent\huge\textbf{Abstracts of talks and sessions}} \\[1em]
%\end{center}

\begin{Abstract}{Sebastian Gutsche \& Max Horn}{TU Kaiserslautern \& JLU Gießen}{How to make a GAP package}

In this hands-on workshop, we will explain the basic requirements for
creating a simple GAP package from scratch. After a brief introduction,
participants can immediately apply this with our help. For this,
participants should bring their laptops and, if present, some code they
want to publish in a package.
%
We also plan to cover more advanced aspects of creating and maintaining
a GAP package.  Which topics are covered in part also depends on requests
by participants. Some possibilities include:
\begin{itemize}[itemsep=0mm]
\item ``Package manuals done right: GAPDoc and AutoDoc'' (this will definitely be covered)
\item Integrating C / C++ code into a GAP package
\item Using GitHub pages as website for your package
\item Automating the package release process with GitHub
\item The importance of package tests and continuous integration
\item Example for automated testing using GitHub and Jenkins
\item ...
\end{itemize}

\end{Abstract}


\begin{Abstract}{Hebert Perez-Roses}{University of Lleida, Spain}{Graph construction via voltage assignment with GAP}
The voltage assignment technique takes a directed "base" graph $B$, and a
group $G$, and constructs another graph $L$ with $|L|=|B||G|$ vertices, where
$|B|$ is the number of vertices of $|B|$. $L$ is usually called the lift of $B$
by $G$, and is a generalization of Cayley graphs. The voltage assignment
technique has been very successful in the construction of large graphs
with small degree and diameter. We are now working on the implementation
of this technique in GAP, and we would like to bring into consideration
of the GAP community the algorithms and data structures used, as well as
to discuss the best alternatives for an efficient implementation.
\end{Abstract}


\begin{Abstract}{Vinay Wagh}{IIT Guwahati, India}{\href{https://github.com/homalg-project/LessGenerators}{LessGenerators} -- finding small generating sets for modules (part of the homalg project)}
	A GAP package called "LessGenerators" has been developed by Mohamed Barakat and myself, to implement the Quillen-Suslin algorithm in computer algebra systems SINGULAR and GAP. The package is part of the homalg project. The aim of this package is to provide a tool for finding a minimal generating set for a given module. The package provides universal implementation in the sense of CASs, i.e. it can use any CAS supported by the homalg project for ring arithmetic.
\end{Abstract}


\end{document}